Check Coverage

### 2021-03-24 analysis/01_filter_by_traits.Rmd

Get biotime data filtered by trait coverage
```{r}
bt_cols <- colnames(biotime_data)[!colnames(biotime_data) %in% 
                                         c("sourceName", "obsID", "scientificName")]
bt_traitfiltered <- biotime_traits %>% 
  select(all_of(bt_cols)) %>%
  rename(species = id)

#save locally and in cache
usethis::use_data(bt_traitfiltered)
pins::pin(bt_traitfiltered, board = "github")
```

>>>>

Get biotime data filtered by trait coverage
```{r}
bt_cols <- colnames(biotime_data)[!colnames(biotime_data) %in% 
                                         c("sourceName", "obsID", "scientificName")]
biotime_traits <- biotime_traits %>% 
  select(all_of(bt_cols)) %>%
  rename(species = id)
```

Split timeseries that have more than one class of species (split up birds and mammals)
```{r}
#get the class of each species
tax_info <- taxadb::filter_id(unique(biotime_traits$species), "itis")
biotime_traits <- biotime_traits %>% 
  left_join(tax_info %>% select(input, class), by = c("species" = "input"))

#find all the studies with more than one taxa type
mix_study <- biotime_traits %>% 
  select(species, class, taxa, study_id) %>% 
  distinct() %>% 
  count(study_id, class, taxa) %>% 
  group_by(study_id) %>%
  filter(n_distinct(class, na.rm = TRUE) > 1) %>% 
  pull(study_id) %>%
  unique()

#split into two different timeseries based on whether they're bird or mammal observations,
#remove years with too few species
mix_split <- biotime_traits %>%
  filter(study_id %in% mix_study) %>%
  mutate(rarefyid = if_else(class == "Aves", paste0(rarefyid, "_bird"), paste0(rarefyid, "_mamm"))) %>%
  group_by(rarefyid, year) %>% 
  filter(n_distinct(species) > 4)

#update that studies that needed to be split with new rarefyid breakdowns
bt_traitfiltered <- biotime_traits %>%
  filter(!study_id %in% mix_study) %>%
  bind_rows(mix_split) %>%
  select(-class)
```

```{r}
#save locally and in cache
usethis::use_data(bt_traitfiltered)
pins::pin(bt_traitfiltered, board = "github")
```
